Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2021-07-30 article/draft.tex
minor updates in the draft

\title{Preliminary Draft}

@@

Title proposition 1: ``Big Tech is censoring me'': using social media data to verify the platforms' regulation policies regarding misinformation.

Title proposition 2: Illustrating Facebook, Twitter and YouTube regulation policies against misinformation with a few chosen examples

Title proposition 3: Misinformation Policies of Mainstream Social Media Platforms: third-party monitoring, methods and illustration.

Title proposition 4: Misinformation related interventions by mainstream social media platforms: third-party monitoring, methods and illustration.

{\color{pink} \noindent N.B: we will redo all the figures (to harmonize the legend, etc.) and the table of contents will be deleted.} 
\tableofcontents

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/globalresearch_domain.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement.jpg}
	%\end{multicols}
\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Data collected via the Twitter API v2 on July $30$, 2021.   }
\label{fig4}
\end{figure}

@@

At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos. But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation. However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended. {\color{pink} mettre cl pour channel level, faire allusion à ce qu'ils disent}. {\color{pink} they do not act on the channel level ... hyper partisan/ misinformation ? } Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general and even harder than on Facebook and Twitter.

@@

Naturally, the design of an intervention by a given online platform in order to moderate content should be adapted to the aimed policy area. Therefor, $classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech. Nevertheless, tackling online misinformation is an active area of research and interventions specifically designed for this $new$ policy area, might be required to avoid undesired effects. Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation. We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.

@@

{ \color{pink} 
\bigskip

@@

\begin{itemize}

@@

\item[Idea 3:] Policies not specific to misinformation. New for smart design (recycling point) - New policy: coordination for informative notices, based on fact-checks.

	\begin{itemize}

		\item Networked public square / private companies / regulations / coordination...

		\item Recommendation: inform about sources, example inform users that this user shared x failed fact-checks.

@@

		\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior. %\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}

@@

	\end{itemize}

\end{itemize}
}

>>>>

\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}

@@

%Title proposition 1: ``Big Tech is censoring me'': using social media data to verify the platforms' regulation policies regarding misinformation.

%Title proposition 2: Illustrating Facebook, Twitter and YouTube regulation policies against misinformation with a few chosen examples

%Title proposition 3: Misinformation Policies of Mainstream Social Media Platforms: third-party monitoring, methods and illustration.

%Title proposition 4: Misinformation related interventions by Facebook, Twitter and YouTube: third-party monitoring, methods and illustration.

%{\color{pink} \noindent N.B: we will redo all the figures (to harmonize the legend, etc.) and the table of contents will be deleted.} 
%\tableofcontents

@@

\begin{figure}[h]
\centering
		\includegraphics[scale=0.27]{../figure/globalresearch_domain.jpg} 
		\includegraphics[scale=0.27]{../figure/globalresearch_domain_engagement.jpg}
\caption{Left Panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Right Panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $30$, $2021$. Data collected via the Twitter API v2 on July $30$, 2021.   }
\label{fig4}
\end{figure}

@@

At the video level, we start at each round with a YouTube video marked as ``False'' and we expected to have a high proportion of misinformation videos. But only {$18.4\%$} of the recommendations corresponded to $misleading$ or {\it hyper-partisan} videos.
This relatively small percentage hints towards that idea that YouTube is probably reducing the visibility of videos containing misinformation. However, when we investigated misinformation at the channel level, we found that videos belonging to channels that are not highly authoritative were being often recommended. In other words, it is likely that YouTube acts on reducing the visibility of videos but not channels, via its recommendation system. Notice that the policy of reducing the visibility of misleading content is hard to prove on YouTube in general, given the complexity of their recommendation algorithm. %and this exercice seems harder Facebook and Twitter.

@@

Naturally, the design of an intervention by a given online platform in order to moderate content should be adapted to the aimed policy area. Therefor, $classic$ interventions such as account suspension and content deletion, might be efficient for policy areas such as Adult Nudity \& Sexual Activity or Hate Speech. Nevertheless, tackling online misinformation is an active area of research and interventions specifically designed for this $new$ policy area, might be required to avoid undesired effects. Namely, account suspensions may have generated a movement of platform migration towards new alternative social media platforms, with little or no content moderation. We invite the reader to see Rogers (2020)~\cite{rogers2020} for an excellent overview about de-platforming and see Robins-Early (2019)~\cite{huffpost} for a news article about Alex Jones's account suspension on Facebook.
{\color{pink} Make point / Recommendation: inform about sources, example inform users that this user/account/page/group/channel has shared x failed fact-checks over a x-months period.}
%\smallskip

@@

%{ \color{pink} 
%\bigskip

@@

@@

%\item[Idea 3:] Policies not specific to misinformation. New for smart design (recycling point) - New policy: coordination for informative notices, based on fact-checks.

		%\item Networked public square / private companies / regulations / coordination...

@@

		%\item Make point that platforms when they take actions regarding misinformation, they rarely cite misinformation as the reason. E.g. beauty of life, coordinated inauthentic behavior. %\href{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}{https://misinforeview.hks.harvard.edu/article/tackling-misinformation-what-researchers-could-do-with-social-media-data/}

@@

	%\end{itemize}

%\end{itemize}
%}
